Procedural generation of levels fot he angry birds videogame using evolutionary computation\\

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
More Comments

\section{Introduction}
Procedural content generation is an interesting subject on the entertainment
area, primarily in the video game industry because of the easines and quickness
provided to generate content for diferent video game projects, in this project a
evolutionary computation-based system is proposed to generate complex content
for videogames based on an evolutionary algorithm and open-ended- evolution.

@@

In Section 2, a background of the subjects used on this project will be
presented, this subjects, while not all being used on by different authors on
their works provide a great help on the development of the proposed system,
Section 3, contains a quick overview of some aspects used by different authors
in order to tackle this problem, their design and basic functionality, in
Section 4 the description of the current state of the project is explained, from
the basis of the development to the diferent menthods that have been used to
progress on the different sections of the project, in Section 5 we explain the
future work of the project, where we are in the development phase and how the
future implementations are to further improve the project and finally, in
Section 6 we present our conclusions

@@

In this Section we provide a quick overview of the literature about the areas
that provide the basis to the development of the current project, this section
is divided in three parts, the fisrt one gives us an explanation of what
procedural content generation entails, the second one provides an explanation on
genetic algorithms and how can they be used to solve optimization problems, and
finally, the third one provides us with an overview of Open-Ended Evolution and
what it means to have an Open-Ended Evolutionary algorithm.

@@

PCG as six focus areas listed as follows:

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=90mm]{Images/ga_life_cycle.png}}
\caption{Life cycle of a genetic algorithm.}
\label{algorithm_model}
\end{figure}

@@

@@

\subsection{Original approach}

Since the algorithm has to generate more complex structures the remaining pieces
of a member of the population have to be used has a starting point, this new
additions to the piece pool are added to the population by the mutation
operation, the objective in the first phase of the project is to generate
structures that are capable of maintaining their own balance as shown on figure
\ref{test_old}, since the objective of open-ended evolution for this project is
to add new bundles to the pool of options the algorithm will first run a
simulation with a group of pieces and after it the ones that were not destroyed
by falling because of gravity will be saved and added to the pool of options.

\begin{figure}[htbp]
\centerline{\includegraphics[width=80mm]{Images/simulation_bef_aft_example.png}}
\caption{Structure at beginning and end of a simulation.}
\label{test_old}
\end{figure}

In order to add a bundle of pieces as a new component first it has to be
measured, an imaginary bounding box is defined by calculating the lengths of all
the pieces, finding the borders of said pieces and find the points that could
define a box around all of them, calculate the height and width then calculate
the center point of said box and calculate the offsets from the center of the
group to the center of each respective piece as shown on figure
\ref{bounding_boc_calc}, this information is needed in order to add it as a new
element so it can be used to place the pieces in their respective new positions
when the files needed for the simulation are being created.

>>>>

\section{Introduction}
Procedural content generation is an interesting subject on the entertainment
industry, primarily in the video game development because of the easines and
quickness provided to generate content for diferent video game projects [ref] .
In this paper an evolutionary content generation system is proposed to generate
levels for the popular Angry Birds video game
\cite{RovioEntertainmentCorporation2009}, taking inspiration in concepts of
open-ended evolution.

@@

% What is the problem?
% How we solve it? (summary)   
% What is learned?

In Section 2, a background of the subjects used on this project will be
presented, this subjects, while not all being used on by different authors on
their works provide a great help on the development of the proposed system,
% Jaime, remember there is no Background need it in this type of paper 
% Maybe that will be the introduction - MG

Section 3, contains a quick overview of some aspects used by different authors
in order to tackle this problem, their design and basic functionality, in
Section 4 the description of the current state of the project is explained, from
the basis of the development to the diferent menthods that have been used to
progress on the different sections of the project, 
% Normaly there is no "Future Work" section is put together with Conclusions - MG
in Section 5 we explain the
future work of the project, where we are in the development phase and how the
future implementations are to further improve the project and finally, in
Section 6 we present our conclusions

@@

In this Section we provide a quick overview of the literature about the areas
that provide the basis to the development of the current project, this section
is divided in three parts, the fisrt one gives us an explanation of what
procedural content generation entails, the second one provides an explanation on
genetic algorithms and how can they be used to solve optimization problems, and
finally, the third one provides us with an overview of Open-Ended Evolution and
% use just one form, I prefer with no first caps open-ended evolution and let's 
% use an abbreviation OEE - MG

what it means to have an Open-Ended Evolutionary algorithm.
% For this conference I think we do not need to define PCG, let's think 
% every one knows what it is. - MG

@@

PCG as six focus areas listed as follows:
% Jaime, you must add references to EVERY THING READ alsewhere : 
% We do not proposed this list, please add a reference. - MG

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=90mm]{Images/ga_life_cycle.png}}
\caption{Life cycle of a genetic algorithm.}
\label{algorithm_model}
\end{figure}
% Maybe this is well known, again our implementation is what we need to describe 
% JJ, what you think?

@@

% Explain a bit about the competition, from the introduction

@@

\subsection{Original approach}
% This sentence needs more work -MG
Since the algorithm has to generate more complex structures the remaining pieces
of a member of the population have to be used has a starting point, this new
% we don't use member of the populations, use proposed solution, candidate solution
% or individual of the population. - MG

additions to the piece pool are added to the population by the mutation
operation, the objective in the first phase of the project is to generate
structures that are capable of maintaining their own balance as shown on figure
\ref{test_old}, since the objective of open-ended evolution for this project is
to add new bundles to the pool of options the algorithm will first run a
simulation with a group of pieces and after it the ones that were not destroyed
by falling because of gravity will be saved and added to the pool of options.

% New pieces are added by mutation? 
% Please give more details to all this - MG

\begin{figure}[htbp]
\centerline{\includegraphics[width=80mm]{Images/simulation_bef_aft_example.png}}
\caption{Structure at beginning and end of a simulation.}
\label{test_old}
\end{figure}
% Here it's explained better, maybe this paragraph should be moved to
% an earlier point - MG

% Needs a few touches - MG
In order to add a bundle of pieces as a new component first it has to be
measured, an imaginary bounding box is defined by calculating the lengths of all
the pieces, finding the borders of said pieces and find the points that could
define a box around all of them, calculate the height and width then calculate
the center point of said box and calculate the offsets from the center of the
group to the center of each respective piece as shown on figure
\ref{bounding_boc_calc}, this information is needed in order to add it as a new
element so it can be used to place the pieces in their respective new positions
when the files needed for the simulation are being created.
